Eye-tracking on the web: lessons learned from replicating 5 experiments

### 2022-01-09 group-d/E4-analysis-replication.Rmd
added data from ryskin et al 2017 for comparison to group d

ggplot(first.move.summary, aes(x=bias, fill=target_type, y=M, ymin=M-SE,ymax=M+SE))+
  geom_col(position=position_dodge(width=0.9), color = "black")+
  geom_errorbar(position=position_dodge(width=0.9), width=0.2)+
  theme_classic()+
  labs(y = "Proportion of first mouse movements")
```

@@

>>>>

ggplot(first.move.summary, aes(x=bias, fill=target_type, y=M, ymin=M-SE,ymax=M+SE))+
  geom_col(position=position_dodge(width=0.9), color = "black")+
  geom_errorbar(position=position_dodge(width=0.9), width=0.2)+
  scale_fill_brewer(palette = "Set1", name = "Location", labels = c("Animal", "Instrument", "Other"))+
  coord_cartesian(ylim = c(0,1))+
  theme_classic()+
  labs(y = "Proportion of first mouse movements", x = NULL)
```

```{r, eval=FALSE}
write_csv(first.move, "output/E4_mouse_data.csv")
```

@@

```{r, eval=FALSE}
write_csv(eyetracking.window.summary.by.trial, "output/E4_eye-tracking_data.csv")
```

### 2022-01-09 manuscript.Rmd
added E2 replication analyses
added data from ryskin et al 2017 for comparison to group d

---
title             : "Eye-tracking on the web: lessons learned from replicating 6 experiments"
shorttitle        : "Just picked a random title: feel free to change"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

@@

<!-- MAJOR TO DOs: 
 - get data from in-lab versions of group A (AJ) and group D (RR)
 - re-run Posner cueing (after we finish analysing the first 5)
 - replicate group D and ?? in lab

@@

- Online data collection is more and more popular & let's us ask new questions

@@

In the present work, we attempted to replicate six eye-tracking studies from the cognitive science literature using the eye-tracking plug-in from `jsPsych`, a Javascript library for running behavioral experiments in a web browser [@deleeuwJsPsychJavaScriptLibrary2015]. The plug-in relies on the `webgazer.js` library for webcam eye-tracking [@papoutsaki2016webgazer]. The goal was to examine the strengths and weaknesses of webcam eye-tracking for common paradigms in cognitive science. The studies were chosen to cover a variety of topic areas (e.g., memory, decision-making, psycholinguistics) and paradigms (two halves of the screen, visual world paradigm with four quadrants, visual world paradigm with "natural" scenes). ...

@@

@@

>>>>

---
title             : "Eye-tracking on the web: lessons learned from replicating 5 experiments"
shorttitle        : "Just picked a random title: feel free to change"

author: 
  - name          : "Josh de Leeuw"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "et al."
    affiliation   : "1,2"
    role:
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Vassar College"
  - id            : "2"
    institution   : "XX"

@@

<!-- MAJOR TO DOs: 
 - get data from in-lab versions of group A (AJ) and group D (RR)
 - replicate group D and A in lab

@@

- Online data collection is more and more popular & let's us ask new questions, test more diverse populations

@@

In the present work, we attempted to replicate five eye-tracking studies from the cognitive science literature using the eye-tracking plug-in from `jsPsych`, a Javascript library for running behavioral experiments in a web browser [@deleeuwJsPsychJavaScriptLibrary2015]. The plug-in relies on the `webgazer.js` library for webcam eye-tracking [@papoutsaki2016webgazer]. The goal was to examine the strengths and weaknesses of webcam eye-tracking for common paradigms in cognitive science. The studies were chosen to cover a variety of topic areas (e.g., memory, decision-making, psycholinguistics) and paradigms (two halves of the screen, visual world paradigm with four quadrants, visual world paradigm with "natural" scenes). ...

@@

```{r E2-analysis-replication, child='group-b/E2-analysis-replication.Rmd'}

@@

```{r E4-analysis-comparsion-to-original-study, child='group-d/E4-analysis-comparison-to-original.Rmd'}

### 2022-01-09 manuscript.tex
added data from ryskin et al 2017 for comparison to group d

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man,floatsintext]{apa6}
\title{Eye-tracking on the web: lessons learned from replicating 6 experiments}
\author{First Author\textsuperscript{1} \& Ernst-August Doelle\textsuperscript{1,2}}
\date{}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Eye-tracking on the web: lessons learned from replicating 6 experiments},
  pdfauthor={First Author1 \& Ernst-August Doelle1,2},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

The authors made the following contributions. First Author: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Ernst-August Doelle: Writing - Review \& Editing.

Correspondence concerning this article should be addressed to First Author, Postal address. E-mail: \href{mailto:my@email.com}{\nolinkurl{my@email.com}}

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Wilhelm-Wundt-University\\\textsuperscript{2} Konstanz Business School}

@@

\begin{itemize}
\item
  Eye-tracking as a key method in cognitive science research
\item
  Online data collection is more and more popular \& let's us ask new questions
\item
  But, concerns over quality + little known about eye-tracking online
\end{itemize}

@@

In the present work, we attempted to replicate six eye-tracking studies from the cognitive science literature using the eye-tracking plug-in from \texttt{jsPsych}, a Javascript library for running behavioral experiments in a web browser (de Leeuw, 2015). The plug-in relies on the \texttt{webgazer.js} library for webcam eye-tracking (Papoutsaki et al., 2016). The goal was to examine the strengths and weaknesses of webcam eye-tracking for common paradigms in cognitive science. The studies were chosen to cover a variety of topic areas (e.g., memory, decision-making, psycholinguistics) and paradigms (two halves of the screen, visual world paradigm with four quadrants, visual world paradigm with ``natural'' scenes). \ldots{}

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man,floatsintext]{apa6}
\title{Eye-tracking on the web: lessons learned from replicating 5 experiments}
\author{Josh de Leeuw\textsuperscript{1} \& et al.\textsuperscript{1,2}}
\date{}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Eye-tracking on the web: lessons learned from replicating 5 experiments},
  pdfauthor={Josh de Leeuw1 \& et al.1,2},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

The authors made the following contributions. Josh de Leeuw: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; et al.: Writing - Review \& Editing.

Correspondence concerning this article should be addressed to Josh de Leeuw, Postal address. E-mail: \href{mailto:my@email.com}{\nolinkurl{my@email.com}}

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Vassar College\\\textsuperscript{2} XX}

@@

\begin{itemize}
\item
  Eye-tracking as a key method in cognitive science research
\item
  Online data collection is more and more popular \& let's us ask new questions, test more diverse populations
\item
  But, concerns over quality + little known about eye-tracking online
\end{itemize}

@@

In the present work, we attempted to replicate five eye-tracking studies from the cognitive science literature using the eye-tracking plug-in from \texttt{jsPsych}, a Javascript library for running behavioral experiments in a web browser (de Leeuw, 2015). The plug-in relies on the \texttt{webgazer.js} library for webcam eye-tracking (Papoutsaki et al., 2016). The goal was to examine the strengths and weaknesses of webcam eye-tracking for common paradigms in cognitive science. The studies were chosen to cover a variety of topic areas (e.g., memory, decision-making, psycholinguistics) and paradigms (two halves of the screen, visual world paradigm with four quadrants, visual world paradigm with ``natural'' scenes). \ldots{}

@@

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/E4-mouse-moves-fig-web-and-orig-1.pdf}
\caption{\label{fig:E4-mouse-moves-fig-web-and-orig}Proportion of first mouse movements by location and verb bias in original dataset (Ryskin et al., 2017) .}
\end{figure}
